```{r setup_participants, include=FALSE}
if (!exists("MANUSCRIPT_MODE") || !MANUSCRIPT_MODE) {
  source("R/packages.R")
  source("R/colors.R")
  source("R/helpers.R")
  source("R/tables.R")
  source("R/plots.R")
  source("R/demographics.R")
  source("R/data-loading.R")
}
```

```{r participants_data, include=FALSE}
demo_s1  <- create_demo_summary(Study1, "Study 1")
demo_s2  <- create_demo_summary(Study2, "Study 2")

demo_all <- demo_s1 %>%
  full_join(demo_s2, by = "Characteristic") %>%
  dplyr::select(Characteristic, `Study 1`, `Study 2`) %>%
  filter(!(`Study 1` == "0 (0%)" & `Study 2` == "0 (0%)"))

s1_n <- nrow(Study1)
s2_n <- nrow(Study2)

s1_r_obs <- cor(s1_core$Religiosity, s1_core$AI_Moral_Frequency, use = "complete.obs")
s2_r_obs <- cor(s2_core$Religiosity, s2_core$AI_Moral_Frequency, use = "complete.obs")
```

## Method
### Participants

All participants were recruited through Prolific. Responses were excluded if they were incomplete, flagged by Qualtrics as likely fraudulent, contained a duplicated Prolific ID, or failed the requisite attention checks. Two pilot studies are reported in the Supplementary Materials. The two pre-registered studies used stratified sampling to ensure balanced representation across sex, age, ethnicity (based on simplified U.S. census categories), and political affiliation. The demographic characteristics for Study 1 and Study 2 are presented in Table 1. 

Study 1 (*N*=`r nrow(Study1)`; pre-registered: <https://aspredicted.org/mv2z-t7dw.pdf>; data collected `r Study1_date`) and Study 2 (*N*=`r nrow(Study2)`; pre-registered: <https://aspredicted.org/z378hg.pdf>; data collected `r Study2_date`) served as the formal replication and extended mediation sample. Target sample sizes were determined by a priori power analyses detailed in the pre-registration documents. Post-hoc power analyses are detailed in the result section. 

All data and supplementary materials are publicly accessible on the Open Science Framework (OSF) at: <https://osf.io/qfv9d/overview?view_only=cfacef5f0d7647458ad928f54f43a54f>. Detailed discrepancies between the pre-registrations and the reported analyses are transparently documented in the Supplementary Materials.

```{r tbl-participants}
#| label: tbl-participants
#| tbl-cap: "Demographic Characteristics of Study 1 and Study 2"

flextable::flextable(demo_all) |>
  flextable::align(j = 1, part = "body", align = "left") |>
  flextable::align(j = 2:3, part = "body", align = "center") |>
  flextable::align(part = "header", align = "center") |>
  flextable::border_remove() |>
  flextable::hline_top(part = "header", border = officer::fp_border(width = 1.5)) |>
  flextable::hline_bottom(part = "header", border = officer::fp_border(width = 1)) |>
  flextable::hline_bottom(part = "body", border = officer::fp_border(width = 1.5)) |>
  flextable::set_table_properties(layout = "autofit", width = 1) |>
  flextable::width(j = 1, width = 2.5) |>
  flextable::width(j = 2:3, width = 1.0)
```

