```{r setup_supp, include=FALSE}
if (!exists("MANUSCRIPT_MODE") || !MANUSCRIPT_MODE) {
  if (!exists("BOOTSTRAP_SIMS")) BOOTSTRAP_SIMS <- 5000
  source("R/packages.R")
  source("R/colors.R")
  source("R/helpers.R")
  source("R/tables.R")
  source("R/plots.R")
  source("R/data-loading.R")
  source("R/supplementary.R")
  source("R/main-analysis.R")
}

# Force full Okabe-Ito color palette for Supplementary Materials
set_color_scheme("color")
```

## Discrepancies from Pre-Registration

Our studies were pre-registered on AsPredicted ([Study 1](https://aspredicted.org/mv2z-t7dw.pdf), [Study 2](https://aspredicted.org/z378hg.pdf)). To maintain a focused presentation of analysis results and prevent scope creep, several analyses and presentation formats deviate from the initial pre-registration documents. @tbl-pre-reg-deviations details these deviations and their justifications.

| Topic / Variable | Pre-registered Plan | Actual Implementation in Main Text | Justification |
|:---|:---|:---|:---|
| **Primary Predictor Choice** | Test both self-reported religiosity and religious behavior frequency. | Focused on **Religious Behavior Score** (RBS) as the primary predictor in main text for Question 3 and 4. Self-reported religiosity results are reported in the Supplementary Materials. | RBS measures concrete frequency of attendance and prayer, anchoring on frequency from never to more than once every day. It also exhibited consistently larger effect sizes.|
| **Outcome (DV) Selection** | Test both frequency of and interest in seeking moral advice from AI chatbots. | Focused on **Frequency** as the primary outcome in the main text. Interest-based results are reported in the Supplementary Materials. | Moving the secondary interest outcome to the supplement reduces main-text length and redundancy, as results for Interest largely mirror those for Frequency. |
| **Model Presentation** | Simple linear regressions for primary hypotheses. | Presented the multiple regression models controlling for demographic covariates in the main text and simple regressionsin the Supplementary Material for Questions 1 and 2. | Control for demographic covariates is more conservative and robust. Moving simple regressions to the supplement reduces main-text table size and redundancy. |
| **Exploratory Parallel Mediation** | Pre-registered parallel mediation as exploratory. | Saturated parallel models with cluster-representative mediators. | The pre-registration did not specify how to structure the parallel models. We chose the candidate mediator explaining the largest proportion of variance from each cluster to minimize criterion contamination among highly correlated scales. |
| **Study 1 General Topic Data** | Collect and analyze general (non-moral) advice seeking and truth objectivity. | Excluded general-topic analyses from the text. | Study 1 collected 12 split hypotheses across general vs. moral and self-reported vs. behavioral religiosity. To prevent the scope from getting out of hand, we omitted general-topic analyses. All raw data and codebooks are published on OSF for public review. |

: Discrepancies from Pre-Registration {#tbl-pre-reg-deviations}

## Variables Used in Study 1 and Study 2

Three measures were revised between studies: *self-reported religiosity* was rescaled from 5-point to 7-point to match the response format of all other measures; *belief in moral objectivity* was changed from a bipolar slider (-50~+50) to a 7-point Likert scale to standardize the response format; and in *perceived authority of AI chatbots as moral advisors*, the word *accurate* was removed (i.e., "trusted authorities for giving accurate moral advice" became "trusted authorities to give moral advice") to better reflect the nature of advice-seeking. Several measures from Study 1 were not included in Study 2 to narrow the research focus and reduce respondent burden. @tbl-methods summarizes all variables used across the two pre-registered studies. 

| Measure | Study 1 | Study 2 |
|:---|:---|:---|
| **Predictors** | | |
| Self-Reported Religiosity | "To what extent do you consider yourself to be religious?" (1=*not at all*, 5=*very*) | "To what extent do you consider yourself to be religious?" (1=*not at all*, 7=*extremely*)  |
| Religious Behavior Score | Average of "How often do you attend religious services/ pray?" (1=*never*, 7=*once a day or more*) | Same as Study 1 |
| **Outcomes** | | |
| Frequency of Seeking Moral Advice from AI Chatbots | "How often do you seek moral advice from an AI chatbot?" (1=*never*, 7=*once a day or more*) | Same as Study 1 |
| Interest in Seeking Moral Advice from AI Chatbots† | "How interested are you in seeking moral advice from an AI chatbot?" (1=*not at all*, 7=*extremely*) | Same as Study 1 |
| **Mediators** | | |
| *(a) Moral consultation disposition* | | |
| Frequency of Seeking Moral Advice | Average frequency of seeking moral advice from 13 non-AI, non-religious sources (1=*never*, 7=*once a day or more*)  | Same as Study 1 |
| Interest in Seeking Moral Advice | Average interest in seeking moral advice from 13 non-AI, non-religious sources (1=*not at all*, 7=*extremely*)  | Same as Study 1 |
| *(b) Epistemic humility* | | |
| Open-Mindedness on Moral Issues | Moral Curiosity Scale [@hartman2022] | Same as Study 1 |
| General Open-Mindedness | Curiosity and Exploration Inventory-II [@kashdan2009] | — |
| Intellectual Humility (MMIH) | Multidimensional Intellectual Humility Scale [@alfano2017] | — |
| Intellectual Humility (CIHS) | Comprehensive Intellectual Humility Scale [@krumrei-mancuso2016] | — |
| *(c) Moral objectivism* | | |
| Belief in Moral Objectivity | "To what extent do you believe that morality is objective or relative?" (slider: −50=*entirely relative* to +50=*entirely objective*) | "Do you believe that, in general, the answers to moral questions are objectively right or wrong, or they are based on people's subjective opinions and preferences?" (1=*definitely subjective*, 7=*definitely objective*) |
| *(d) Positive perception of AI chatbots* | | |
| Perceived Authority of AI Chatbots | "Chatbots/AI assistants are trusted authorities for giving accurate moral advice" (1=*strongly disagree*, 7=*strongly agree*) | "Do you believe that chatbots/AI assistants are trusted authorities to give moral advice?" (1=*strongly disagree*, 7=*strongly agree*) |
| Perceived Valence of AI Chatbots | "Chatbots/AI assistants are ______ at giving moral advice" (1 = *extremely bad*, 7 = *extremely good*) | — |
| *(e) Tendency to anthropomorphize AI chatbots* | | |
| Tendency to Anthropomorphize AI | — | Adapted Anthropomorphism Subscale of the Godspeed Questionnaire [@bartneck2009] |
| *(f) Other personality traits* | | |
| Fear of Negative Judgment | — | Brief Fear of Negative Evaluation Scale [@leary1983] |
| Self-Reflective Tendencies | — | Self-reflection subscale of the Self-Reflection and Insight Scale [@grant2002] |
| Deference to Authority (MFQ-2) | — | Authority subscale of the Moral Foundation Questionnaire (MFQ-2) [@atari2023] |
| Deference to Authority (MAC-Q) | — | Deference subscale of the Morality-as-Cooperation Questionnaire [@curry2019] |
| **Moderator** | | |
| Access to AI Chatbots | — | "How accessible do you find AI chatbots for giving moral advice or guidance?" (1=*not at all accessible*, 7=*completely accessible*) |
| Overall Access to Moral Advice Sources | — | Average accessibility across 13 non-AI, non-religious moral advice sources (1=*not at all accessible*, 7=*completely accessible*) |

: Variables Used in Study 1 and Study 2 {#tbl-methods}

*Note: In Study 1, clusters (a) and (c) also collected non-moral-specific parallel measures (e.g., general frequency of and interest in seeking advice from non-AI, non-religious sources; belief in factual objectivity with "truth" in place of "morality"). These measures are included in the datasets, but the analyses are omitted for brevity, as the present study focuses on moral-specific constructs. Study 2 removed these non-moral-specific measures to reduce participant fatigue and narrow research focus.*

## Demographic Characteristics of Included Participants in Study 1 and Study 2

The demographic characteristics of the included participants in Study 1 and Study 2 are presented in @tbl-participants.

```{r participants_data, include=FALSE}
demo_s1  <- create_demo_summary(Study1, "Study 1")
demo_s2  <- create_demo_summary(Study2, "Study 2")

demo_all <- demo_s1 %>%
  full_join(demo_s2, by = "Characteristic") %>%
  dplyr::select(Characteristic, `Study 1`, `Study 2`) %>%
  filter(!(`Study 1` == "0 (0%)" & `Study 2` == "0 (0%)"))
```

```{r tbl-participants}
#| label: tbl-participants
#| tbl-cap: "Demographic Characteristics of Included Participants in Study 1 and Study 2"

flextable::flextable(demo_all) |>
  flextable::align(j = 1, part = "body", align = "left") |>
  flextable::align(j = 2:3, part = "body", align = "center") |>
  flextable::align(part = "header", align = "center") |>
  flextable::border_remove() |>
  flextable::hline_top(part = "header", border = officer::fp_border(width = 1.5)) |>
  flextable::hline_bottom(part = "header", border = officer::fp_border(width = 1)) |>
  flextable::hline_bottom(part = "body", border = officer::fp_border(width = 1.5)) |>
  flextable::set_table_properties(layout = "autofit", width = 1) |>
  flextable::width(j = 1, width = 2.5) |>
  flextable::width(j = 2:3, width = 1.0)
```

## Sources of Moral Advice

### Source Ranking Plots

#### Frequency of Seeking Moral Advice

```{r supp-freq-data, include=FALSE}
s1_freq_summary <- summarise_sources(s1_moral_freq)
s2_freq_summary <- summarise_sources(s2_moral_freq)
```

```{r fig-supp-freq, fig.width=12, fig.height=6}
#| label: fig-supp-freq
#| fig-cap: "Frequency of Seeking Moral Advice by Source"
#| apa-note: "Ratings use a 7-point scale (1 = Never, 7 = Once a day or more). Error bars represent ±1 SE. The dashed line indicates the mean frequency across all external non-AI, non-religious sources (excluding Praying or Meditation, Religious Texts, and Religious Leaders to avoid criterion contamination with the religiosity predictor)."

p_s1_freq <- plot_source_ranking(s1_freq_summary, FREQ_LABELS) + ggtitle("Study 1")
p_s2_freq <- plot_source_ranking(s2_freq_summary, FREQ_LABELS) + ggtitle("Study 2")
p_s1_freq | p_s2_freq
```

#### Interest in Seeking Moral Advice

```{r supp-interest-data, include=FALSE}
s1_interest_summary <- summarise_sources(s1_moral_interest)
s2_interest_summary <- summarise_sources(s2_moral_interest)
```

```{r fig-supp-interest, fig.width=12, fig.height=6}
#| label: fig-supp-interest
#| fig-cap: "Interest in Seeking Moral Advice by Source"
#| apa-note: "Ratings use a 7-point scale (1 = Not at all, 7 = Extremely). Error bars represent ±1 SE. The dashed line indicates the mean interest across all external non-AI, non-religious sources (excluding Praying or Meditation, Religious Texts, and Religious Leaders to avoid criterion contamination with the religiosity predictor)."

p_s1_int <- plot_source_ranking(s1_interest_summary, INTEREST_LABELS) + ggtitle("Study 1")
p_s2_int <- plot_source_ranking(s2_interest_summary, INTEREST_LABELS) + ggtitle("Study 2")
p_s1_int | p_s2_int
```

#### Accessibility of Moral Advice Sources (Study 2 Only)

```{r supp-access-data, include=FALSE}
s2_access_summary <- summarise_sources(s2_moral_access)
```

```{r fig-supp-access, fig.width=8, fig.height=6, fig.align='center'}
#| label: fig-supp-access
#| fig-cap: "Study 2: Accessibility of Each Source of Moral Advice"
#| apa-note: "Ratings use a 7-point scale (1 = Not at all accessible, 7 = Completely accessible). Error bars represent ±1 SE. The dashed line indicates the mean accessibility across all external non-AI, non-religious sources (excluding Praying or Meditation, Religious Texts, and Religious Leaders to avoid criterion contamination with the religiosity predictor)."

plot_source_ranking(s2_access_summary, ACCESS_LABELS)
```

### Source Correlation Heatmaps

#### Frequency of Seeking Moral Advice

```{r fig-supp-freq-heatmap-s1, fig.width=10, fig.height=9}
#| label: fig-supp-freq-heatmap-s1
#| fig-cap: "Study 1: Correlation Heatmap — Frequency of Seeking Moral Advice Across Sources"
#| apa-note: "Pearson correlation matrix for the 18 moral advice sources. Sources are ordered by hierarchical clustering. Cells display pairwise r values with significance indicators: * p < .05, ** p < .01, *** p < .001."

plot_cor_heatmap(s1_moral_freq, title = "Study 1")
```

```{r fig-supp-freq-heatmap-s2, fig.width=10, fig.height=9}
#| label: fig-supp-freq-heatmap-s2
#| fig-cap: "Study 2: Correlation Heatmap — Frequency of Seeking Moral Advice Across Sources"
#| apa-note: "Pearson correlation matrix for the 18 moral advice sources. Sources are ordered by hierarchical clustering. Cells display pairwise r values with significance indicators: * p < .05, ** p < .01, *** p < .001."

plot_cor_heatmap(s2_moral_freq, title = "Study 2")
```

#### Interest in Seeking Moral Advice

```{r fig-supp-interest-heatmap-s1, fig.width=10, fig.height=9}
#| label: fig-supp-interest-heatmap-s1
#| fig-cap: "Study 1: Correlation Heatmap — Interest in Seeking Moral Advice Across Sources"
#| apa-note: "Pearson correlation matrix for the 18 moral advice sources. Sources are ordered by hierarchical clustering. Cells display pairwise r values with significance indicators: * p < .05, ** p < .01, *** p < .001."

plot_cor_heatmap(s1_moral_interest, title = "Study 1")
```

```{r fig-supp-interest-heatmap-s2, fig.width=10, fig.height=9}
#| label: fig-supp-interest-heatmap-s2
#| fig-cap: "Study 2: Correlation Heatmap — Interest in Seeking Moral Advice Across Sources"
#| apa-note: "Pearson correlation matrix for the 18 moral advice sources. Sources are ordered by hierarchical clustering. Cells display pairwise r values with significance indicators: * p < .05, ** p < .01, *** p < .001."

plot_cor_heatmap(s2_moral_interest, title = "Study 2")
```

## Correlation Analyses

### Predictor → AI Moral Frequency

@tbl-supp-freq-correlation and @fig-supp-freq-scatter present the correlation analyses between the religiosity predictors (Self-Reported Religiosity and Religious Behavior Score) and the frequency of seeking moral advice from AI chatbots across Study 1 and Study 2.

```{r tbl-supp-freq-correlation}
#| label: tbl-supp-freq-correlation
#| tbl-cap: "Pearson Correlations Between Religiosity Predictors and Frequency of Seeking Moral Advice From AI Chatbots"

make_cor_flextable(table_correlation_freq)
```

```{r fig-supp-freq-scatter, fig.width=12, fig.height=10}
#| label: fig-supp-freq-scatter
#| fig-cap: "Religious Behavior Score and Self-Reported Religiosity Predicting Frequency of Seeking Moral Advice from AI Chatbots"
#| apa-note: "Each panel shows jittered raw data points, a linear regression fit with 95% confidence band, and a LOESS trend line with 95% confidence band."

p_freq_rs_s1 <- plot_scatter_cor(s1_core, "R_Score", "AI_Moral_Frequency",
                x_label = "Religious Behavior Score",
                y_label = "Frequency of Seeking Moral Advice from AI") +
  ggtitle("Study 1: Religious Behavior Score \u2192 Frequency")

p_freq_rs_s2 <- plot_scatter_cor(s2_core, "R_Score", "AI_Moral_Frequency",
                x_label = "Religious Behavior Score",
                y_label = "Frequency of Seeking Moral Advice from AI") +
  ggtitle("Study 2: Religious Behavior Score \u2192 Frequency")

p_freq_rel_s1 <- plot_scatter_cor(s1_core, "Religiosity", "AI_Moral_Frequency",
                 x_label = "Self-Reported Religiosity",
                 y_label = "Frequency of Seeking Moral Advice from AI") +
  scale_x_continuous(name = "Self-Reported Religiosity", breaks = 1:5) +
  ggtitle("Study 1: Religiosity \u2192 Frequency")

p_freq_rel_s2 <- plot_scatter_cor(s2_core, "Religiosity", "AI_Moral_Frequency",
                 x_label = "Self-Reported Religiosity",
                 y_label = "Frequency of Seeking Moral Advice from AI") +
  scale_x_continuous(name = "Self-Reported Religiosity", breaks = 1:7) +
  ggtitle("Study 2: Religiosity \u2192 Frequency")

(p_freq_rs_s1 | p_freq_rs_s2) / (p_freq_rel_s1 | p_freq_rel_s2)
```

### Predictor → AI Moral Interest

@tbl-supp-int-correlation and @fig-supp-int-scatter present the correlation analyses between the religiosity predictors (Self-Reported Religiosity and Religious Behavior Score) and the interest in seeking moral advice from AI chatbots across Study 1 and Study 2.

```{r tbl-supp-int-correlation}
#| label: tbl-supp-int-correlation
#| tbl-cap: "Pearson Correlations Between Religiosity Predictors and Interest in Seeking Moral Advice From AI Chatbots"

make_cor_flextable(table_correlation_int)
```

```{r fig-supp-int-scatter, fig.width=12, fig.height=10}
#| label: fig-supp-int-scatter
#| fig-cap: "Religious Behavior Score and Self-Reported Religiosity Predicting Interest in Seeking Moral Advice from AI Chatbots"
#| apa-note: "Each panel shows jittered raw data points, a linear regression fit with 95% confidence band, and a LOESS trend line with 95% confidence band."

p_int_s1 <- plot_scatter_cor(s1_core, "R_Score", "AI_Moral_Interest",
               x_label = "Religious Behavior Score",
               y_label = "Interest in Seeking Moral Advice from AI") +
  ggtitle("Study 1: Religious Behavior Score \u2192 Interest")

p_int_s2 <- plot_scatter_cor(s2_core, "R_Score", "AI_Moral_Interest",
               x_label = "Religious Behavior Score",
               y_label = "Interest in Seeking Moral Advice from AI") +
  ggtitle("Study 2: Religious Behavior Score \u2192 Interest")

p_int_s1 <- plot_scatter_cor(s1_core, "Religiosity", "AI_Moral_Interest",
               x_label = "Self-Reported Religiosity",
               y_label = "Interest in Seeking Moral Advice from AI") +
  scale_x_continuous(name = "Self-Reported Religiosity", breaks = 1:5) +
  ggtitle("Study 1: Religiosity \u2192 Interest")

p_int_s2 <- plot_scatter_cor(s2_core, "Religiosity", "AI_Moral_Interest",
               x_label = "Self-Reported Religiosity",
               y_label = "Interest in Seeking Moral Advice from AI") +
  scale_x_continuous(name = "Self-Reported Religiosity", breaks = 1:7) +
  ggtitle("Study 2: Religiosity \u2192 Interest")

(p_int_s1 | p_int_s2) / (p_int_s1 | p_int_s2)
```

## Regression Analyses

### Self-Reported Religiosity → AI Moral Frequency

@tbl-rel-freq-regression presents both simple linear regression models (without demographic covariates) and multiple linear regression models for Self-Reported Religiosity predicting Frequency of Seeking Moral Advice from AI Chatbots.

```{r tbl-rel-freq-regression}
#| label: tbl-rel-freq-regression
#| tbl-cap: "Self-Reported Religiosity Predicting Frequency of Seeking Moral Advice from AI Chatbots"
#| apa-note: "All regression coefficients are standardized. Model 1 = simple regression. Model 2 = multiple regression controlling for age, education, income, SES, and political orientation."

make_study_reg_table(reg_rows_rel_freq)
```

### Religious Behavior Score → AI Moral Frequency

@tbl-rs-freq-regression presents both simple linear regression models (without demographic covariates) and multiple linear regression models for Religious Behavior Score predicting Frequency of Seeking Moral Advice from AI Chatbots.

```{r tbl-rs-freq-regression}
#| label: tbl-rs-freq-regression
#| tbl-cap: "Religious Behavior Score Predicting Frequency of Seeking Moral Advice from AI Chatbots"
#| apa-note: "All regression coefficients are standardized. Model 1 = simple regression. Model 2 = multiple regression controlling for age, education, income, SES, and political orientation."

make_study_reg_table(reg_rows_rs_freq)
```

### Self-Reported Religiosity → AI Moral Interest

@tbl-rel-int-regression presents both simple linear regression models (without demographic covariates) and multiple linear regression models for Self-Reported Religiosity predicting Interest in Seeking Moral Advice from AI Chatbots.

```{r tbl-rel-int-regression}
#| label: tbl-rel-int-regression
#| tbl-cap: "Self-Reported Religiosity Predicting Interest in Seeking Moral Advice From AI Chatbots"
#| apa-note: "All regression coefficients are standardized. Model 1 = simple regression. Model 2 = multiple regression controlling for age, education, income, SES, and political orientation."

make_study_reg_table(reg_rows_rel_int)
```

### Religious Behavior Score → AI Moral Interest

@tbl-rs-int-regression presents both simple linear regression models (without demographic covariates) and multiple linear regression models for Religious Behavior Score predicting Interest in Seeking Moral Advice from AI Chatbots.

```{r tbl-rs-int-regression}
#| label: tbl-rs-int-regression
#| tbl-cap: "Religious Behavior Score Predicting Interest in Seeking Moral Advice from AI Chatbots"
#| apa-note: "All regression coefficients are standardized. Model 1 = simple regression. Model 2 = multiple regression controlling for age, education, income, SES, and political orientation."

make_study_reg_table(reg_rows_rs_int)
```

## Mediation Analyses

### Path-A Regression Analyses

#### Self-Reported Religiosity → Candidate Mediators

@tbl-rel-patha-s1 and @tbl-rel-patha-s2 report the regression of Self-Reported Religiosity onto each candidate mediator. These results underline both the Self-Reported Religiosity → Frequency and Self-Reported Religiosity → Interest mediation pathways, as the Religiosity → Mediator path is identical across both.

```{r tbl-rel-patha-s1}
#| label: tbl-rel-patha-s1
#| tbl-cap: "Study 1: Self-Reported Religiosity Predicting Each Candidate Mediator"
#| apa-note: "All regression coefficients are standardized. Model 1 = simple regression. Model 2 = multiple regression controlling for age, education, income, SES, and political orientation. These estimates apply to both the Self-Reported Religiosity → Frequency and Self-Reported Religiosity → Interest mediation pathways."

path_a_table_rel_s1
```

```{r tbl-rel-patha-s2}
#| label: tbl-rel-patha-s2
#| tbl-cap: "Study 2: Self-Reported Religiosity Predicting Each Candidate Mediator"
#| apa-note: "All regression coefficients are standardized. Model 1 = simple regression. Model 2 = multiple regression controlling for age, education, income, SES, and political orientation. These estimates apply to both the Self-Reported Religiosity → Frequency and Self-Reported Religiosity → Interest mediation pathways."

path_a_table_rel_s2
```

#### Religious Behavior Score → Candidate Mediators

@tbl-rs-patha-s1 and @tbl-rs-patha-s2 report the regression of Religious Behavior Score onto each candidate mediator. Because the predictor → mediator path is identical regardless of the downstream outcome, these estimates underline both the Religious Behavior Score → Frequency and Religious Behavior Score → Interest mediation pathways.

```{r tbl-rs-patha-s1}
#| label: tbl-rs-patha-s1
#| tbl-cap: "Study 1: Religious Behavior Score Predicting Each Candidate Mediator"
#| apa-note: "All regression coefficients are standardized. Model 1 = simple regression. Model 2 = multiple regression controlling for age, education, income, SES, and political orientation. These estimates apply to both the Religious Behavior Score → Frequency and Religious Behavior Score → Interest mediation pathways."

path_a_table_rs_s1
```

```{r tbl-rs-patha-s2}
#| label: tbl-rs-patha-s2
#| tbl-cap: "Study 2: Religious Behavior Score Predicting Each Candidate Mediator"
#| apa-note: "All regression coefficients are standardized. Model 1 = simple regression. Model 2 = multiple regression controlling for age, education, income, SES, and political orientation. These estimates apply to both the Religious Behavior Score → Frequency and Religious Behavior Score → Interest mediation pathways."

path_a_table_rs_s2
```

### Individual Mediation Analyses

For the individual mediation analyses, candidate mediators were included only if they were significantly associated with the focal predictor (applying the same conservative Bonferroni correction used in the main manuscript: $p < .05 / `r ncol(s1_mediators)` = `r sub("^0", "", sprintf("%.4f", 0.05 / ncol(s1_mediators)))`$ in Study 1; $p < .05 / `r ncol(s2_mediators)` = `r sub("^0", "", sprintf("%.4f", 0.05 / ncol(s2_mediators)))`$ in Study 2) in either the simple (Model 1) or demographic-adjusted (Model 2) regression models.

#### Self-Reported Religiosity → Mediator → AI Moral Frequency

```{r tbl-rel-freq-s1-mediation}
#| label: tbl-rel-freq-s1-mediation
#| tbl-cap: "Study 1: Individual Statistical Mediation (Indirect Effect) Analyses (Self-Reported Religiosity → Mediator → AI Moral Frequency)"
#| apa-note: "All paths show standardized coefficients (β) and percentile bootstrap 95% confidence intervals based on 5,000 bootstrap simulations. Only mediators significant (p < .05) in at least one regression model are included."

mediation_table_from_results(ind_mediation_rel_freq_s1, selected_mediators = names(rep_mediators_rel_freq_s1$mediators))
```

```{r tbl-rel-freq-s2-mediation}
#| label: tbl-rel-freq-s2-mediation
#| tbl-cap: "Study 2: Individual Statistical Mediation (Indirect Effect) Analyses (Self-Reported Religiosity → Mediator → AI Moral Frequency)"
#| apa-note: "All paths show standardized coefficients (β) and percentile bootstrap 95% confidence intervals based on 5,000 bootstrap simulations. Only mediators significant (p < .05) in at least one regression model are included."

mediation_table_from_results(ind_mediation_rel_freq_s2, selected_mediators = names(rep_mediators_rel_freq_s2$mediators))
```

#### Religious Behavior Score → Mediator → AI Moral Frequency

```{r tbl-rs-freq-s1-mediation}
#| label: tbl-rs-freq-s1-mediation
#| tbl-cap: "Study 1: Individual Statistical Mediation (Indirect Effect) Analyses (Religious Behavior Score → Mediator → AI Moral Frequency)"
#| apa-note: "All paths show standardized coefficients (β) and percentile bootstrap 95% confidence intervals based on 5,000 bootstrap simulations. Only mediators significant (adjusted *p < .05) in at least one regression model are included."

mediation_table_from_results(ind_mediation_rs_freq_s1, selected_mediators = names(rep_mediators_rs_freq_s1$mediators))
```

```{r tbl-rs-freq-s2-mediation}
#| label: tbl-rs-freq-s2-mediation
#| tbl-cap: "Study 2: Individual Statistical Mediation (Indirect Effect) Analyses (Religious Behavior Score → Mediator → AI Moral Frequency)"
#| apa-note: "All paths show standardized coefficients (β) and percentile bootstrap 95% confidence intervals based on 5,000 bootstrap simulations. Only mediators significant (adjusted *p < .05) in at least one regression model are included."

mediation_table_from_results(ind_mediation_rs_freq_s2, selected_mediators = names(rep_mediators_rs_freq_s2$mediators))
```

#### Self-Reported Religiosity → Mediator → AI Moral Interest

```{r tbl-rel-int-s1-mediation}
#| label: tbl-rel-int-s1-mediation
#| tbl-cap: "Study 1: Individual Statistical Mediation (Indirect Effect) Analyses (Self-Reported Religiosity → Mediator → AI Moral Interest)"
#| apa-note: "All paths show standardized coefficients (β) and percentile bootstrap 95% confidence intervals based on 5,000 bootstrap simulations. Only mediators significant (p < .05) in at least one regression model are included."

mediation_table_from_results(ind_mediation_rel_int_s1, selected_mediators = names(rep_mediators_rel_int_s1$mediators))
```

```{r tbl-rel-int-s2-mediation}
#| label: tbl-rel-int-s2-mediation
#| tbl-cap: "Study 2: Individual Statistical Mediation (Indirect Effect) Analyses (Self-Reported Religiosity → Mediator → AI Moral Interest)"
#| apa-note: "All paths show standardized coefficients (β) and percentile bootstrap 95% confidence intervals based on 5,000 bootstrap simulations. Only mediators significant (p < .05) in at least one regression model are included."

mediation_table_from_results(ind_mediation_rel_int_s2, selected_mediators = names(rep_mediators_rel_int_s2$mediators))
```

#### Religious Behavior Score → Mediator → AI Moral Interest

```{r tbl-rs-int-s1-mediation}
#| label: tbl-rs-int-s1-mediation
#| tbl-cap: "Study 1: Individual Statistical Mediation (Indirect Effect) Analyses (Religious Behavior Score → Mediator → AI Moral Interest)"
#| apa-note: "All paths show standardized coefficients (β) and percentile bootstrap 95% confidence intervals based on 5,000 bootstrap simulations. Only mediators significant (p < .05) in at least one regression model are included."

mediation_table_from_results(ind_mediation_rs_int_s1, selected_mediators = names(rep_mediators_rs_int_s1$mediators))
```

```{r tbl-rs-int-s2-mediation}
#| label: tbl-rs-int-s2-mediation
#| tbl-cap: "Study 2: Individual Statistical Mediation (Indirect Effect) Analyses (Religious Behavior Score → Mediator → AI Moral Interest)"
#| apa-note: "All paths show standardized coefficients (β) and percentile bootstrap 95% confidence intervals based on 5,000 bootstrap simulations. Only mediators significant (p < .05) in at least one regression model are included."

mediation_table_from_results(ind_mediation_rs_int_s2, selected_mediators = names(rep_mediators_rs_int_s2$mediators))
```

### Parallel Mediation Analyses {#sec-supp-parallel}

```{r setup-supp-parallel-summaries, include=FALSE}
# --- Pre-formatted parallel SEM model fit strings ---
summary_str_rel_freq_s1 <- fmt_parallel_summary_apa(summary_parallel_rel_freq_s1, "AI moral frequency", full = FALSE)
summary_str_rel_freq_s2 <- fmt_parallel_summary_apa(summary_parallel_rel_freq_s2, full = FALSE)

summary_str_rs_freq_s1  <- fmt_parallel_summary_apa(summary_parallel_rs_freq_s1, "AI moral frequency", full = FALSE)
summary_str_rs_freq_s2  <- fmt_parallel_summary_apa(summary_parallel_rs_freq_s2, full = FALSE)

summary_str_rel_int_s1  <- fmt_parallel_summary_apa(summary_parallel_rel_int_s1, "AI moral interest", full = FALSE)
summary_str_rel_int_s2  <- fmt_parallel_summary_apa(summary_parallel_rel_int_s2, full = FALSE)

summary_str_rs_int_s1   <- fmt_parallel_summary_apa(summary_parallel_rs_int_s1, "AI moral interest", full = FALSE)
summary_str_rs_int_s2   <- fmt_parallel_summary_apa(summary_parallel_rs_int_s2, full = FALSE)
```

#### Self-Reported Religiosity → AI Moral Frequency

In Study 1, the parallel statistical model `r summary_str_rel_freq_s1`. In Study 2, the model `r summary_str_rel_freq_s2`. Path diagrams (@fig-rel-freq-parallel-s1, @fig-rel-freq-parallel-s2) and full parameter estimate tables (@tbl-rel-freq-s1-parallel, @tbl-rel-freq-s2-parallel) present these results.

```{r fig-rel-freq-parallel-s1, fig.width=6.5, fig.height=5}
#| label: fig-rel-freq-parallel-s1
#| fig-cap: "Study 1: Parallel Mediation Diagram (Self-Reported Religiosity → AI Moral Frequency)"
#| apa-note: "Edge labels show unstandardized b (standardized β in parentheses) and unstandardized percentile bootstrap 95% CI in brackets based on 5,000 bootstrap simulations. Mediator intercorrelations included in the model but omitted for clarity."

make_path_diagram(
  mediator_labels = rep_mediators_rel_freq_s1$names,
  coefs = extract_path_coefs(parallel_rel_freq_s1, length(rep_mediators_rel_freq_s1$names))
)
```

```{r tbl-rel-freq-s1-parallel}
#| label: tbl-rel-freq-s1-parallel
#| tbl-cap: "Study 1: Parameter Estimates — Parallel Mediation (Self-Reported Religiosity → AI Moral Frequency)"
#| apa-note: "Columns: Path = model relationship; b = unstandardized coefficient; β = standardized coefficient; SE = standard error; 95% CI LL/UL = lower and upper bounds of the percentile bootstrap 95% confidence interval for the unstandardized coefficient (b); p = p-value. Row types: Predictor → Mediator rows are a paths; Mediator → Outcome rows are b paths; the direct row is the c′ path (predictor → outcome controlling for mediators); rows with ~~ are residual covariances between mediators; Indirect via rows are specific indirect effects (a × b); Total indirect effect is the sum of all specific indirect effects."

fmt_all_estimates_table(estimates_parallel_rel_freq_s1)
```

```{r fig-rel-freq-parallel-s2, fig.width=6.5, fig.height=6.5}
#| label: fig-rel-freq-parallel-s2
#| fig-cap: "Study 2: Parallel Mediation Diagram (Self-Reported Religiosity → AI Moral Frequency)"
#| apa-note: "Edge labels show unstandardized b (standardized β in parentheses) and unstandardized percentile bootstrap 95% CI in brackets based on 5,000 bootstrap simulations. Mediator intercorrelations included in the model but omitted for clarity."

make_path_diagram(
  mediator_labels = rep_mediators_rel_freq_s2$names,
  coefs = extract_path_coefs(parallel_rel_freq_s2, length(rep_mediators_rel_freq_s2$names))
)
```

```{r tbl-rel-freq-s2-parallel}
#| label: tbl-rel-freq-s2-parallel
#| tbl-cap: "Study 2: Parameter Estimates — Parallel Mediation (Self-Reported Religiosity → AI Moral Frequency)"
#| apa-note: "Columns: Path = model relationship; b = unstandardized coefficient; β = standardized coefficient; SE = standard error; 95% CI LL/UL = lower and upper bounds of the percentile bootstrap 95% confidence interval for the unstandardized coefficient (b); p = p-value. Row types: Predictor → Mediator rows are a paths; Mediator → Outcome rows are b paths; the direct row is the c′ path (predictor → outcome controlling for mediators); rows with ~~ are residual covariances between mediators; Indirect via rows are specific indirect effects (a × b); Total indirect effect is the sum of all specific indirect effects."

fmt_all_estimates_table(estimates_parallel_rel_freq_s2)
```

#### Religious Behavior Score → AI Moral Frequency

In Study 1, the parallel statistical model `r summary_str_rs_freq_s1`. In Study 2, the model `r summary_str_rs_freq_s2`. Path diagrams (@fig-rs-freq-parallel-s1, @fig-rs-freq-parallel-s2) and full parameter estimate tables (@tbl-rs-freq-s1-parallel, @tbl-rs-freq-s2-parallel) present these results.

```{r fig-rs-freq-parallel-s1, fig.width=6.5, fig.height=5.1}
#| label: fig-rs-freq-parallel-s1
#| fig-cap: "Study 1: Parallel Mediation Diagram (Religious Behavior Score → AI Moral Frequency)"
#| apa-note: "Edge labels show unstandardized b (standardized β in parentheses) and unstandardized percentile bootstrap 95% CI in brackets based on 5,000 bootstrap simulations. Mediator intercorrelations included in the model but omitted for clarity."

make_path_diagram(
  mediator_labels = rep_mediators_rs_freq_s1$names,
  coefs = extract_path_coefs(parallel_rs_freq_s1, length(rep_mediators_rs_freq_s1$names))
)
```

```{r tbl-rs-freq-s1-parallel}
#| label: tbl-rs-freq-s1-parallel
#| tbl-cap: "Study 1: Parameter Estimates — Parallel Mediation (Religious Behavior Score → AI Moral Frequency)"
#| apa-note: "Columns: Path = model relationship; b = unstandardized coefficient; β = standardized coefficient; SE = standard error; 95% CI LL/UL = lower and upper bounds of the percentile bootstrap 95% confidence interval for the unstandardized coefficient (b); p = p-value. Row types: Predictor → Mediator rows are a paths; Mediator → Outcome rows are b paths; the direct row is the c′ path (predictor → outcome controlling for mediators); rows with ~~ are residual covariances between mediators; Indirect via rows are specific indirect effects (a × b); Total indirect effect is the sum of all specific indirect effects."

fmt_all_estimates_table(estimates_parallel_rs_freq_s1)
```

```{r fig-rs-freq-parallel-s2, fig.width=6.5, fig.height=6}
#| label: fig-rs-freq-parallel-s2
#| fig-cap: "Study 2: Parallel Mediation Diagram (Religious Behavior Score → AI Moral Frequency)"
#| apa-note: "Edge labels show unstandardized b (standardized β in parentheses) and unstandardized percentile bootstrap 95% CI in brackets based on 5,000 bootstrap simulations. Mediator intercorrelations included in the model but omitted for clarity."

make_path_diagram(
  mediator_labels = rep_mediators_rs_freq_s2$names,
  coefs = extract_path_coefs(parallel_rs_freq_s2, length(rep_mediators_rs_freq_s2$names))
)
```

```{r tbl-rs-freq-s2-parallel}
#| label: tbl-rs-freq-s2-parallel
#| tbl-cap: "Study 2: Parameter Estimates — Parallel Mediation (Religious Behavior Score → AI Moral Frequency)"
#| apa-note: "Columns: Path = model relationship; b = unstandardized coefficient; β = standardized coefficient; SE = standard error; 95% CI LL/UL = lower and upper bounds of the percentile bootstrap 95% confidence interval for the unstandardized coefficient (b); p = p-value. Row types: Predictor → Mediator rows are a paths; Mediator → Outcome rows are b paths; the direct row is the c′ path (predictor → outcome controlling for mediators); rows with ~~ are residual covariances between mediators; Indirect via rows are specific indirect effects (a × b); Total indirect effect is the sum of all specific indirect effects."

fmt_all_estimates_table(estimates_parallel_rs_freq_s2)
```

#### Self-Reported Religiosity → AI Moral Interest

In Study 1, the parallel statistical model `r summary_str_rel_int_s1`. In Study 2, the model `r summary_str_rel_int_s2`. Path diagrams (@fig-rel-int-parallel-s1, @fig-rel-int-parallel-s2) and full parameter estimate tables (@tbl-rel-int-s1-parallel, @tbl-rel-int-s2-parallel) present these results.

```{r fig-rel-int-parallel-s1, fig.width=6.5, fig.height=5}
#| label: fig-rel-int-parallel-s1
#| fig-cap: "Study 1: Parallel Mediation Diagram (Self-Reported Religiosity → AI Moral Interest)"
#| apa-note: "Edge labels show unstandardized b (standardized β in parentheses) and unstandardized percentile bootstrap 95% CI in brackets based on 5,000 bootstrap simulations. Mediator intercorrelations included in the model but omitted for clarity."

make_path_diagram(
  mediator_labels = rep_mediators_rel_int_s1$names,
  coefs = extract_path_coefs(parallel_rel_int_s1, length(rep_mediators_rel_int_s1$names))
)
```

```{r tbl-rel-int-s1-parallel}
#| label: tbl-rel-int-s1-parallel
#| tbl-cap: "Study 1: Parameter Estimates — Parallel Mediation (Self-Reported Religiosity → AI Moral Interest)"
#| apa-note: "Columns: Path = model relationship; b = unstandardized coefficient; β = standardized coefficient; SE = standard error; 95% CI LL/UL = lower and upper bounds of the percentile bootstrap 95% confidence interval for the unstandardized coefficient (b); p = p-value. Row types: Predictor → Mediator rows are a paths; Mediator → Outcome rows are b paths; the direct row is the c′ path (predictor → outcome controlling for mediators); rows with ~~ are residual covariances between mediators; Indirect via rows are specific indirect effects (a × b); Total indirect effect is the sum of all specific indirect effects."

fmt_all_estimates_table(estimates_parallel_rel_int_s1)
```

```{r fig-rel-int-parallel-s2, fig.width=6.5, fig.height=6.5}
#| label: fig-rel-int-parallel-s2
#| fig-cap: "Study 2: Parallel Mediation Diagram (Self-Reported Religiosity → AI Moral Interest)"
#| apa-note: "Edge labels show unstandardized b (standardized β in parentheses) and unstandardized percentile bootstrap 95% CI in brackets based on 5,000 bootstrap simulations. Mediator intercorrelations included in the model but omitted for clarity."

make_path_diagram(
  mediator_labels = rep_mediators_rel_int_s2$names,
  coefs = extract_path_coefs(parallel_rel_int_s2, length(rep_mediators_rel_int_s2$names))
)
```

```{r tbl-rel-int-s2-parallel}
#| label: tbl-rel-int-s2-parallel
#| tbl-cap: "Study 2: Parameter Estimates — Parallel Mediation (Self-Reported Religiosity → AI Moral Interest)"
#| apa-note: "Columns: Path = model relationship; b = unstandardized coefficient; β = standardized coefficient; SE = standard error; 95% CI LL/UL = lower and upper bounds of the percentile bootstrap 95% confidence interval for the unstandardized coefficient (b); p = p-value. Row types: Predictor → Mediator rows are a paths; Mediator → Outcome rows are b paths; the direct row is the c′ path (predictor → outcome controlling for mediators); rows with ~~ are residual covariances between mediators; Indirect via rows are specific indirect effects (a × b); Total indirect effect is the sum of all specific indirect effects."

fmt_all_estimates_table(estimates_parallel_rel_int_s2)
```

#### Religious Behavior Score → AI Moral Interest

In Study 1, the parallel statistical model `r summary_str_rs_int_s1`. In Study 2, the model `r summary_str_rs_int_s2`. Path diagrams (@fig-rs-int-parallel-s1, @fig-rs-int-parallel-s2) and full parameter estimate tables (@tbl-rs-int-s1-parallel, @tbl-rs-int-s2-parallel) present these results.

```{r fig-rs-int-parallel-s1, fig.width=6.5, fig.height=5}
#| label: fig-rs-int-parallel-s1
#| fig-cap: "Study 1: Parallel Mediation Diagram (Religious Behavior Score → AI Moral Interest)"
#| apa-note: "Edge labels show unstandardized b (standardized β in parentheses) and unstandardized percentile bootstrap 95% CI in brackets based on 5,000 bootstrap simulations. Mediator intercorrelations included in the model but omitted for clarity."

make_path_diagram(
  mediator_labels = rep_mediators_rs_int_s1$names,
  coefs = extract_path_coefs(parallel_rs_int_s1, length(rep_mediators_rs_int_s1$names))
)
```

```{r tbl-rs-int-s1-parallel}
#| label: tbl-rs-int-s1-parallel
#| tbl-cap: "Study 1: Parameter Estimates — Parallel Mediation (Religious Behavior Score → AI Moral Interest)"
#| apa-note: "Columns: Path = model relationship; b = unstandardized coefficient; β = standardized coefficient; SE = standard error; 95% CI LL/UL = lower and upper bounds of the percentile bootstrap 95% confidence interval for the unstandardized coefficient (b); p = p-value. Row types: Predictor → Mediator rows are a paths; Mediator → Outcome rows are b paths; the direct row is the c′ path (predictor → outcome controlling for mediators); rows with ~~ are residual covariances between mediators; Indirect via rows are specific indirect effects (a × b); Total indirect effect is the sum of all specific indirect effects."

fmt_all_estimates_table(estimates_parallel_rs_int_s1)
```

```{r fig-rs-int-parallel-s2, fig.width=6.5, fig.height=5}
#| label: fig-rs-int-parallel-s2
#| fig-cap: "Study 2: Parallel Mediation — Self-Reported Religiosity → AI Moral Interest"
#| apa-note: "Edge labels show unstandardized b (standardized β in parentheses) and unstandardized percentile bootstrap 95% CI in brackets based on 5,000 bootstrap simulations. Mediator intercorrelations included in the model but omitted for clarity."

make_path_diagram(
  mediator_labels = rep_mediators_rs_int_s2$names,
  coefs = extract_path_coefs(parallel_rs_int_s2, length(rep_mediators_rs_int_s2$names))
)
```

```{r tbl-rs-int-s2-parallel}
#| label: tbl-rs-int-s2-parallel
#| tbl-cap: "Study 2: Parameter Estimates — Parallel Mediation (Religious Behavior Score → AI Moral Interest)"
#| apa-note: "Columns: Path = model relationship; b = unstandardized coefficient; β = standardized coefficient; SE = standard error; 95% CI LL/UL = lower and upper bounds of the percentile bootstrap 95% confidence interval for the unstandardized coefficient (b); p = p-value. Row types: Predictor → Mediator rows are a paths; Mediator → Outcome rows are b paths; the direct row is the c′ path (predictor → outcome controlling for mediators); rows with ~~ are residual covariances between mediators; Indirect via rows are specific indirect effects (a × b); Total indirect effect is the sum of all specific indirect effects."

fmt_all_estimates_table(estimates_parallel_rs_int_s2)
```

## Moderation Analyses {#sec-supp-moderation}

For each moderation model, we test both AI chatbot access and overall access to non-AI sources as moderators (Study 2 only).

```{r supp-mod-quantiles, include=FALSE}
ai_vals      <- quantile(s2_core$AI_Moral_Access, probs = c(0.16, 0.50, 0.84), na.rm = TRUE)
overall_vals <- quantile(s2_core$Moral_Access,    probs = c(0.16, 0.50, 0.84), na.rm = TRUE)
```

### Self-Reported Religiosity × Access → AI Moral Frequency

```{r tbl-rel-freq-moderation}
#| label: tbl-rel-freq-moderation
#| tbl-cap: "Moderation Analysis: Self-Reported Religiosity Predicting AI Moral Frequency Moderated by Access"

make_moderation_table(
  moderation_rel_freq_s2_ai,
  moderation_rel_freq_s2_overall,
  pred_name = "Self-Reported Religiosity",
  mod1_name = "AI Chatbot Access",
  mod2_name = "Overall Source Access"
)
```

```{r fig-rel-freq-moderation, fig.width=12, fig.height=5}
#| label: fig-rel-freq-moderation
#| fig-cap: "Self-Reported Religiosity and Frequency of Seeking AI Moral Advice Moderated by Access"
#| apa-note: "Each panel shows predicted regression slopes at low (16th percentile), medium (50th percentile), and high (84th percentile) access levels with 95% confidence bands."

plt_rel_ai_freq <- make_mod_plot(moderation_rel_freq_s2_ai, "AI_Moral_Access", ai_vals,
                                  "AI Chatbot Access",
                                  x_var = "Religiosity",
                                  x_label = "Self-Reported Religiosity") +
  ggtitle("AI Chatbot Access")
plt_rel_ov_freq <- make_mod_plot(moderation_rel_freq_s2_overall, "Moral_Access", overall_vals,
                                  "Overall Source Access",
                                  x_var = "Religiosity",
                                  x_label = "Self-Reported Religiosity") +
  ggtitle("Overall Source Access")

plt_rel_ai_freq | plt_rel_ov_freq
```

### Religious Behavior Score × Access → AI Moral Frequency

```{r tbl-rs-freq-moderation-supp}
#| label: tbl-rs-freq-moderation-supp
#| tbl-cap: "Moderation Analysis: Religious Behavior Score Predicting AI Moral Frequency Moderated by Access"

make_moderation_table(
  moderation_rs_freq_s2_ai,
  moderation_rs_freq_s2_overall,
  pred_name = "Religious Behavior Score",
  mod1_name = "AI Chatbot Access",
  mod2_name = "Overall Source Access"
)
```

```{r fig-rs-freq-moderation-supp, fig.width=12, fig.height=5}
#| label: fig-rs-freq-moderation-supp
#| fig-cap: "Religious Behavior Score and Frequency of Seeking AI Moral Advice Moderated by Access"
#| apa-note: "Each panel shows predicted regression slopes at low (16th percentile), medium (50th percentile), and high (84th percentile) access levels with 95% confidence bands."

plt_rs_ai_freq <- make_mod_plot(moderation_rs_freq_s2_ai, "AI_Moral_Access", ai_vals,
                                "AI Chatbot Access",
                                x_var = "R_Score",
                                x_label = "Religious Behavior Score",
                                y_label = "Frequency of Seeking Moral Advice from AI Chatbots") +
  ggtitle("AI Chatbot Access")
plt_rs_ov_freq <- make_mod_plot(moderation_rs_freq_s2_overall, "Moral_Access", overall_vals,
                                "Overall Source Access",
                                x_var = "R_Score",
                                x_label = "Religious Behavior Score",
                                y_label = "Frequency of Seeking Moral Advice from AI Chatbots") +
  ggtitle("Overall Source Access")

plt_rs_ai_freq | plt_rs_ov_freq
```

### Self-Reported Religiosity × Access → AI Moral Interest

```{r tbl-rel-int-moderation}
#| label: tbl-rel-int-moderation
#| tbl-cap: "Moderation Analysis: Self-Reported Religiosity Predicting AI Moral Interest Moderated by Access"

make_moderation_table(
  moderation_rel_int_s2_ai,
  moderation_rel_int_s2_overall,
  pred_name = "Self-Reported Religiosity",
  mod1_name = "AI Chatbot Access",
  mod2_name = "Overall Source Access"
)
```

```{r fig-rel-int-moderation, fig.width=12, fig.height=5}
#| label: fig-rel-int-moderation
#| fig-cap: "Self-Reported Religiosity and Interest in Seeking AI Moral Advice Moderated by Access"
#| apa-note: "Each panel shows predicted regression slopes at low (16th percentile), medium (50th percentile), and high (84th percentile) access levels with 95% confidence bands."

plt_rel_ai_int <- make_mod_plot(moderation_rel_int_s2_ai, "AI_Moral_Access", ai_vals,
                                 "AI Chatbot Access",
                                 x_var = "Religiosity",
                                 x_label = "Self-Reported Religiosity",
                                 y_label = "Interest in Seeking Moral Advice from AI Chatbots") +
  ggtitle("AI Chatbot Access")
plt_rel_ov_int <- make_mod_plot(moderation_rel_int_s2_overall, "Moral_Access", overall_vals,
                                 "Overall Source Access",
                                 x_var = "Religiosity",
                                 x_label = "Self-Reported Religiosity",
                                 y_label = "Interest in Seeking Moral Advice from AI Chatbots") +
  ggtitle("Overall Source Access")

plt_rel_ai_int | plt_rel_ov_int
```

### Religious Behavior Score × Access → AI Moral Interest

```{r tbl-rs-int-moderation}
#| label: tbl-rs-int-moderation
#| tbl-cap: "Moderation Analysis: Religious Behavior Score Predicting AI Moral Interest Moderated by Access"

make_moderation_table(
  moderation_rs_int_s2_ai,
  moderation_rs_int_s2_overall,
  pred_name = "Religious Behavior Score",
  mod1_name = "AI Chatbot Access",
  mod2_name = "Overall Source Access"
)
```

```{r fig-rs-int-moderation, fig.width=12, fig.height=5}
#| label: fig-rs-int-moderation
#| fig-cap: "Religious Behavior Score and Interest in Seeking AI Moral Advice Moderated by Access"
#| apa-note: "Each panel shows predicted regression slopes at low (16th percentile), medium (50th percentile), and high (84th percentile) access levels with 95% confidence bands."

plt_rs_ai_int <- make_mod_plot(moderation_rs_int_s2_ai, "AI_Moral_Access", ai_vals,
                                "AI Chatbot Access",
                                y_label = "Interest in Seeking Moral Advice from AI Chatbots") +
  ggtitle("AI Chatbot Access")
plt_rs_ov_int <- make_mod_plot(moderation_rs_int_s2_overall, "Moral_Access", overall_vals,
                                "Overall Source Access",
                                y_label = "Interest in Seeking Moral Advice from AI Chatbots") +
  ggtitle("Overall Source Access")

plt_rs_ai_int | plt_rs_ov_int
```

## Study Variable Correlation Analysis

The full correlation matrices for Study 1 and Study 2 are visualized in the heatmaps below (@fig-supp-core-heatmap-s1 and @fig-supp-core-heatmap-s2). 

```{r fig-supp-core-heatmap-s1, fig.width=14, fig.height=13}
#| label: fig-supp-core-heatmap-s1
#| fig-cap: "Study 1: Correlation Heatmap — Study Variables"
#| apa-note: "Pearson correlation matrix for all study variables. Variables are ordered by hierarchical clustering. Cells display pairwise r values with significance indicators: * p < .05, ** p < .01, *** p < .001."

plot_cor_heatmap(s1_core, var_names = S1_CORE_NAMES, title = "Study 1", text_size = 2.5)
```

```{r fig-supp-core-heatmap-s2, fig.width=14, fig.height=13}
#| label: fig-supp-core-heatmap-s2
#| fig-cap: "Study 2: Correlation Heatmap — Study Variables"
#| apa-note: "Pearson correlation matrix for all study variables. Variables are ordered by hierarchical clustering. Cells display pairwise r values with significance indicators: * p < .05, ** p < .01, *** p < .001."

plot_cor_heatmap(s2_core, var_names = S2_CORE_NAMES, title = "Study 2", text_size = 2.5)
```

## Pilot Studies {#sec-supp-pilot-studies}

### Demographic Characteristics of Included Participants in Pilot Study 1 and Pilot Study 2

Two pilot studies provided initial evidence for the relationship between religiosity and seeking moral advice from AI chatbots. Pilot 1 (*N* = `r nrow(P1)`, `r P1_date`) and Pilot 2 (*N* = `r nrow(P2)`, `r P2_date`) recruited participants through Prolific. In both pilot studies, seeking moral guidance from AI chatbots was assessed with the item *"How much do you usually seek moral guidance from Chatbot/AI assistant?"* (1 = *None at all*, 5 = *A great deal*), and self-reported religiosity was measured on a scale of 1 (*Not at all*) to 4 (*Very*). Demographic characteristics for the pilot studies are presented in @tbl-pilot-participants.

```{r pilot_demo_data, include=FALSE}
demo_p1  <- create_demo_summary(P1, "Pilot 1")
demo_p2  <- create_demo_summary(P2, "Pilot 2")

demo_pilot <- demo_p1 %>%
  full_join(demo_p2, by = "Characteristic") %>%
  dplyr::select(Characteristic, `Pilot 1`, `Pilot 2`) %>%
  filter(!(`Pilot 1` == "0 (0%)" & `Pilot 2` == "0 (0%)"))
```

```{r tbl-pilot-participants}
#| label: tbl-pilot-participants
#| tbl-cap: "Demographic Characteristics of Pilot Studies"

flextable::flextable(demo_pilot) |>
  flextable::align(j = 1, part = "body", align = "left") |>
  flextable::align(j = 2:3, part = "body", align = "center") |>
  flextable::align(part = "header", align = "center") |>
  flextable::border_remove() |>
  flextable::hline_top(part = "header", border = officer::fp_border(width = 1.5)) |>
  flextable::hline_bottom(part = "header", border = officer::fp_border(width = 1)) |>
  flextable::hline_bottom(part = "body", border = officer::fp_border(width = 1.5)) |>
  flextable::set_table_properties(layout = "autofit", width = 1) |>
  flextable::width(j = 1, width = 2.5) |>
  flextable::width(j = 2:3, width = 1.0)
```

### Correlation Analyses

```{r tbl-pilot-correlation}
#| label: tbl-pilot-correlation
#| tbl-cap: "Pilot Studies: Pearson Correlations Between Self-Reported Religiosity and Seeking Moral Guidance From AI Chatbots"

cor_tbl_pilot <- data.frame(
  Study = c("Pilot 1", "Pilot 2"),
  N     = c(nrow(P1), nrow(P2)),
  r     = fmt_no_zero(c(pilot_cor_p1$estimate, pilot_cor_p2$estimate), 2),
  t     = round(c(pilot_cor_p1$statistic, pilot_cor_p2$statistic), 2),
  df    = c(pilot_cor_p1$parameter, pilot_cor_p2$parameter),
  p     = c(apa_p(pilot_cor_p1$p.value), apa_p(pilot_cor_p2$p.value)),
  check.names = FALSE
)
names(cor_tbl_pilot) <- c("Study", "N", "r", "t", "df", "p")

make_cor_flextable(cor_tbl_pilot)
```

```{r fig-pilot-scatter, fig.width=12, fig.height=5}
#| label: fig-pilot-scatter
#| fig-cap: "Pilot Studies: Self-Reported Religiosity and Seeking Moral Guidance from AI Chatbots"
#| apa-note: "Each panel shows jittered raw data points, a linear regression fit with 95% confidence band, and a LOESS trend line with 95% confidence band."

p1_plot_data <- P1[P1$Religiosity %% 1 == 0, ]
p2_plot_data <- P2[P2$Religiosity %% 1 == 0, ]

p1_plt <- plot_scatter_cor(p1_plot_data, "Religiosity", "Moral.Source._13",
             x_label = "Self-Reported Religiosity",
             y_label = "Seeking Moral Guidance from AI Chatbots") +
  scale_x_continuous(name = "Self-Reported Religiosity", breaks = 1:4) +
  ggtitle("Pilot 1")

p2_plt <- plot_scatter_cor(p2_plot_data, "Religiosity", "Q115_15",
             x_label = "Self-Reported Religiosity",
             y_label = "Seeking Moral Guidance from AI Chatbots") +
  scale_x_continuous(name = "Self-Reported Religiosity", breaks = 1:4) +
  ggtitle("Pilot 2")

p1_plt | p2_plt
```

### Regression Analyses

```{r tbl-pilot-regression}
#| label: tbl-pilot-regression
#| tbl-cap: "Pilot Studies: Self-Reported Religiosity Predicting Seeking Moral Guidance From AI Chatbots"
#| apa-note: "All regression coefficients are standardized. Model 1 = simple regression. Model 2 = multiple regression controlling for age, education, income, SES, and political orientation."

make_study_reg_table(reg_rows_pilot)
```
